Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-27 NEUROC/sec7-conclusion.tex
更新致谢信息.

This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], the China NSF Grants [grant number U1811461, 62072230], and the Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.

>>>>

This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No. U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Alibaba Innovative Resarch Project, and the program B for outstanding PhD candidate of Nanjing University.
